---
title: "Herring Analysis"
author: "Tomasz Kubat"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, results='hide'}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE) # knitr setup

globalVariables = list() # create empty list for global variables
globalVariables[['wd']] <- '/home/anaconda/Projects/HerringAnalysis'
# globalVariables[['wd']] <- dirname(rstudioapi::getSourceEditorContext()$path) # get working directory

setwd(globalVariables$wd) # set working directory
globalVariables[['requiredPackages']] <- c('dplyr', 'Hmisc', 'corrplot', 'knitr', 'ggplot2', 'rmarkdown') # set required packages

# print(getwd())
source('scripts/loadFunctions.R') # load user-defined functions
source('scripts/loadData.R') # load and clean data
```

# Summary

Bla bla bla

```{r summaryDynamicPlot}

# create object for dynamic plor
# boxplot(dataCleaned$length ~ dataCleaned$monthNr)


# ggDP <- ggplot(dataCleaned, aes(x=monthNr, y=length)) +
#  geom_point()
  
  
# print plot


```




# Dataset

## General information

We operate on herrings dataset which contains of `r dim(dataRaw)[1]` observations devided into `r dim(dataRaw)[2]` variables. 


## Cleaning the data

Performed operations:  
* **renaming columns** to ensure better data understanding.  
* **imputations** were performed to improve data quality. Removing some variables with missing data is rather a wird option, because percent of NAs in dataset is rather insignifficant (~3% on average, differs among the variables).  
* **removing highly correlated variables**. Two variables, *length* and *monthNr*, were excluded from reduction operation, due to being independent and factor, respectively. Removed correlated to:  
- *herrinsNumber*: *fryLeftAnnualPrc* (-0.71), *fryLeftPrc* (-0.51), *fryAnnualSize* (0.37)  
- *planktonChel1*: *planktonLcop1* (0.93), *northAtlanticOscillation* (-0.5)
- *planktonChel2*:  *planktonLcop2* (0.86)  



```{r dataCorrelation}
dataCorr <- cor(select(dataImputed, -c(length,monthNr))) # calculate correlation for numeric variables (exclude length (y) and monthnr (factor))
corrplot(dataCorr, method = 'circle', insig = 'blank', order = 'alphabet', type = 'upper') # draw corplot
# round(dataImputedCorr,2)
```




Bellow is presented the summary (a descriptive statistics) about the clened dataset.

```{r dataSummary}

library(tidyr)
library(purrr)
dataCleaned %>%
  keep(is.numeric) %>%
  gather() %>%
  ggplot(aes(value)) + 
  facet_wrap(~ key, scales = "free_x") +
  geom_histogram()


# summary(dataCleaned)
```













# Analysis

dodac wykres dynamiczny w podziale na miesiace
Graphs
Interaktywny wykres lub animację prezentującą zmianę rozmiaru śledzi w czasie.

# Annotations

* Missing the information about the year complicates performing analysis.
* To prepare report were used packages listed below: `r sort(sessionInfo()$basePkgs)`
