---
title: "Herring Analysis"
author: "Tomasz Kubat"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, results='hide'}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE) # knitr setup

globalVariables = list() # create empty list for global variables
globalVariables[['wd']] <- '/home/anaconda/Projects/HerringAnalysis'
# globalVariables[['wd']] <- dirname(rstudioapi::getSourceEditorContext()$path) # get working directory

setwd(globalVariables$wd) # set working directory
globalVariables[['requiredPackages']] <- c('dplyr', 'Hmisc', 'corrplot', 'knitr', 'ggplot2', 'rmarkdown') # set required packages

# print(getwd())
source('scripts/loadFunctions.R') # load user-defined functions
source('scripts/loadData.R') # load and clean data
```

# Summary

Bla bla bla

# Data

## General info
We use observations `r dim(dataRaw)[1]` devided into `r dim(dataRaw)[2]` variables.

## Rawa data

The following paragraph presents some information about **raw dataset**.
```{r dataRaw}

summary(dataRaw)
# plot(dataRaw)


```
## Cleaned data

The following paragraph presents some information about **cleaned dataset**.
Performed operations:
* aaa
* bbb

```{r dataCleaned}

summary(dataRaw)
# plot(dataCleaned)
# number of imputed rows

```

# Analysis

dodac wykres dynamiczny w podziale na miesiace
zbadaj korelacje wartosci (dej wykres matrix corplot)
Graphs
Interaktywny wykres lub animację prezentującą zmianę rozmiaru śledzi w czasie.

# Apendix

* **used (loaded) packages:** `r sort(sessionInfo()$basePkgs)`
